\newpage
\section{Abstract}
\section{Introduction}
\subsection{Motivation}
\vspace{-1.5mm}
(why are you investigating the problem, domain,industry)
\vspace{-2mm}
\subsection{Problem Statement}
\vspace{-1.5mm}
 (what is being investigated, precision is important)
\vspace{-2mm}
\subsection{Objectives}
\vspace{-1.5mm}
(what are you hoping to achieve with your investigation, who will it benefit?)
\newpage
\section{Background Material}
\subsection{Subject 1}
\vspace{-1.5mm}
(Some information about Subject 1)
\vspace{-2mm}
\subsection{Subject 2}
\vspace{-1.5mm}
(Some information about Subject 2)
\subsection{Subject n}
\vspace{-1.5mm}
(Some more information)
\newpage
\section{Methods \& Methodology}
\subsection{How did we approach the problem?}
\vspace{-1.5mm}
\subsection{What techniques are used in analysis of results}
\newpage
\section{Results Obtained/Lessons Learned}
\subsection{Under What Conditions}
\vspace{-1.5mm}
\subsection{Constraints}
\vspace{-1.5mm}
\subsection{Quality - adequate? Subpar? And why?}
\newpage
\section{Conclusions And Future Works}
\subsection{Suggested improvements -- things that you would change to be more applicable to solving the problem in the future. Things that you would change and why?}
\vspace{-1.5mm}
\subsection{Limitations to solution -- suggest scenarios where the solution offered is NOT applicable, or does not work well.}
\vspace{-1.5mm}
\subsection{ Applications in real world -- list out some situations where your solutions can be applied immediately, speak to the benefits}
\vspace{-1.5mm}
\subsection{ Conclusion -- briefly summarize findings in one paragraph or less.}